EvoSwarm: A Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-05-14 draft.tex
Commit before the Big Move

The trend concerning the parallel execution multi-population algorithms goes from
earlier hardware-based implementations using transputers
\cite{gorges1990explicit} through 
multi-core systems \cite{Serrano2008,lai2019adaptive} to multi-threaded \cite{merelo2019scaling} ones.
And recently the focus has been on exploiting a higher number of processing
units by using GPUs \cite{tan2015survey,li2007efficient}, or distributed
systems, including web-based \cite{JSON} systems,
map-reduce \cite{fazenda2012} implementations,  grids \cite{munawar2010design,Gonzalez09},
voluntary computing systems \cite{MilkyWay}, % Maybe add one of our own voluntary computing references? - JJ
and, more importantly, cloud computing
\cite{GValdez2015,salza2019speed,valenzuela2015implementing,FlexGP}. Cloud computing has become the standard way of running
enterprise applications, not only because of the convenience of the
pay-as-you-go model or the non-existent sunk cost of physical facilities, but also because
it offers a way of describing the infrastructure as part of the code, so that it
is much easier to reproduce results and this has been a boon for scientific
computing.  However,  cloud computing has also been evolving, going from simply
putting on virtual machines elsewhere than on premises old-style monolithic applications, that is, applications
built on a single stack of services that communicate by layers, to microservices
\cite{microservices} and serverless architectures \cite{varghese2018next,Varghese2018849} that favor the parallel and asynchronous communication of
heterogeneous resources; in the process, a new methodology for designing {\em cloud
native applications} has been created, with brand new methods and
techniques \cite{Baldini2016287}. In these architectures, services or even
functions are seen as independent processing nodes, departing from the monolithic
and even distributed paradigms, and becoming a loosely coupled collection of {\em
stateless functions} \cite{malawski2017serverless}, that react to events and
only come into existence while they are doing some processing.
Systems developed with the patterns outlined above have the
properties of a reactive system \cite{boner2014reactive} and they are commonly
more flexible, fault-tolerant, and scalable. % Some properies and reference - Mario  
% Again, you have to justify the need for a reactive architecture and define it before this paragraph - JJ

@@

\section{Multi-population methods} % Is this part of the state of the
\label{multi}
                                % art? - JJ
% This the Background for the design decisions, but I think is also needed
% to better understand the state of the art.
% I don't know. Maybe it should be directly merged with the state of
% the art, if there's some essential to our paper it should go to the
% introduction - JJ

@@

\subsection{Comparison with other cloud-based works} 
\label{comparison}

@@

% Maybe these three sections should be merged; they are all experimental set up and the two next ones start with "experimental"
% (and he next one too) - JJ
% done - Mario
% But also change title? - JJ
% Experimental design of a container-based application or something like that - JJ 
% Like it - M
\section{Experimental design of a container-based application} 
\label{docker}

@@

\subsection{EvoSwarm from the developer point of view}

@@

\section{Deploying to a cloud provider}
\label{cloud-aws}
Container-based applications describe the deployment of loosely coupled
processes in a consistent and portable way, in every phase of the life cycle of
an application, from development through testing to production independently on
the kind of infrastructure. The term cloud-native describes these
container-based environments because they are deployed on an infrastructure that
abstracts the underlying compute, storage, and networking primitives. This
infrastructure does need to be a cloud provider; it could be a developer's
laptop, a single server, or a production environment. When we deploy a
cloud-native application to a cloud provider, we have some more options to
choose:

>>>>

The trend concerning the parallel execution multi-population algorithms goes from
earlier hardware-based implementations using transputers
\cite{gorges1990explicit} through 
multi-core systems \cite{Serrano2008,lai2019adaptive} to multi-threaded \cite{merelo2019scaling} ones.
And recently the focus has been on exploiting a higher number of processing
units by using GPUs \cite{tan2015survey,li2007efficient}, or distributed
systems, including web-based \cite{JSON} systems,
map-reduce \cite{fazenda2012} implementations,  grids \cite{munawar2010design,Gonzalez09},
voluntary computing systems \cite{MilkyWay,merelo2016nodio}, 
and, more importantly, cloud computing
\cite{GValdez2015,salza2019speed,valenzuela2015implementing,FlexGP}. Cloud computing has become the standard way of running
enterprise applications, not only because of the convenience of the
pay-as-you-go model or the non-existent sunk cost of physical facilities, but also because
it offers a way of describing the infrastructure as part of the code, so that it
is much easier to reproduce results and this has been a boon for scientific
computing.  However,  cloud computing has also been evolving, going from simply
putting on virtual machines elsewhere than on premises old-style monolithic applications, that is, applications
built on a single stack of services that communicate by layers, to microservices
\cite{microservices} and serverless architectures \cite{varghese2018next,Varghese2018849} that favor the parallel and asynchronous communication of
heterogeneous resources; in the process, a new methodology for designing {\em cloud
native applications} has been created, with brand new methods and
techniques \cite{Baldini2016287}. In these architectures, services or even
functions are seen as independent processing nodes, departing from the monolithic
and even distributed paradigms, and becoming a loosely coupled collection of {\em
stateless functions} \cite{malawski2017serverless}, that react to events and
only come into existence while they are doing some processing.
Systems developed with the patterns outlined above have the
properties of a reactive system \cite{boner2014reactive} and they are commonly
more flexible, fault-tolerant, and scalable. % Some properies and reference - Mario  
% Again, you have to justify the need for a reactive architecture and define it before this paragraph - JJ

@@

\section{Multi-population Methods} % Is this part of the state of the
\label{multi}
                                % art? - JJ
% This the Background for the design decisions, but I think is also needed
% to better understand the state of the art.
% I don't know. Maybe it should be directly merged with the state of
% the art, if there's some essential to our paper it should go to the
% introduction - JJ

@@

\subsection{Comparison with Other Cloud-based Works} 
\label{comparison}

@@

% Maybe these three sections should be merged; they are all experimental set up and the two next ones start with "experimental"
% (and he next one too) - JJ
% done - Mario
% But also change title? - JJ
% Experimental design of a container-based application or something like that - JJ 
% Like it - M
\section{Experimental Design of a Container-based Application} 
\label{docker}

@@

\subsection{EvoSwarm from the Developer Point of View}

@@

\section{Deploying to a Cloud Provider}
\label{cloud-aws}
Container-based applications describe the deployment of loosely coupled
processes in a consistent and portable way, in every phase of the life cycle of
an application, from development through testing to production independently on
the kind of infrastructure. The term cloud-native describes these
container-based environments because they are deployed on an infrastructure that
abstracts the underlying compute, storage, and networking primitives. This
infrastructure does need to be a cloud provider; it could be a developer's
laptop, a single server, or a production environment. When we deploy a
cloud-native application to a cloud provider, we have some more options to
choose:
